---
title: "p8105_hw1_sd3730"
author: "Stacey Dai"
output: github_document
---

```{r setup, include = FALSE}
library(tidyverse)
data("penguins", package = "palmerpenguins")
```


# Problem 1

The `penguins` dataset contains information about the measurements of penguins. There are `r nrow(penguins)` rows and `r ncol(penguins)` columns in the dataset. Some important variables include:

- `species`: The species of the penguins, such as `r paste(unique(penguins$species), collapse = ", ")`.
- `island`: The island where the penguins were observed (`r paste(unique(penguins$island), collapse = ", ")`).

Other variables include `bill_length_mm` and `bill_depth_mm`, which describe the length and depth of the bills of penguins in millimeters, respectively. The variable `sex` refers to the gender of the penguins and `year` represents the year that the penguin data was collected. 

The variable `flipper_length_mm` represents the length of the penguins' flippers in millimeters. The mean flipper length is `r mean(penguins$flipper_length_mm, na.rm = TRUE)` mm.

## Scatterplot of flipper length by bill length
```{r yx_scatter, warning = FALSE}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + 
  geom_point()
```

```{r save-plot, echo = FALSE, warning = FALSE}
ggsave("penguins_scatterplot.png", height = 4, width = 6)
```


# Problem 2

This code creates a tibble named hw1_df that contains four columns of mixed data types for analysis.

```{r hw1_p2}
hw1_df = tibble(
 numeric_var = rnorm(10),              
  logical_var = rnorm(10) > 0,
  character_var = sample(letters[1:10], 10),
  factor_var = factor(sample(letters[1:3], 10, replace = TRUE))
)

```{r display_table, echo = FALSE}
print(hw1_df)
