---
title: "p8105_hw1_sd3730"
author: "Stacey Dai"
output: github_document
---

# Problem 0.1

This code is used to set up the RMarkdown file and load necessary packages.
```{r setup, message = FALSE}
library(tidyverse)
data("penguins", package = "palmerpenguins")
```

# Problem 1

The `penguins` dataset contains information about the measurements of penguins. There are `r nrow(penguins)` rows and `r ncol(penguins)` columns in the dataset. Some important variables include:

- `species`: The species of the penguins, such as `r paste(unique(penguins$species), collapse = ", ")`.
- `island`: The island where the penguins were observed (`r paste(unique(penguins$island), collapse = ", ")`).

Other variables include `bill_length_mm` and `bill_depth_mm`, which describe the length and depth of the bills of penguins in millimeters, respectively. The variable `sex` refers to the gender of the penguins and `year` represents the year that the penguin data was collected. 

The variable `flipper_length_mm` represents the length of the penguins' flippers in millimeters. The mean flipper length is `r mean(penguins$flipper_length_mm, na.rm = TRUE)` mm.

## Scatterplot of flipper length by bill length

This code creates a scatterplot using the `ggplot` function to visualize the relationship between bill length and flipper length. Here's the code:

```{r yx_scatter, warning = FALSE}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + 
  geom_point()
```

The resulting scatterplot helps to visually assess any correlations between bill length and flipper length, while also illustrating the differences across species of penguins.

```{r save-plot, echo = FALSE, warning = FALSE}
ggsave("penguins_scatterplot.png", height = 4, width = 6)
```


# Problem 2

This code creates a tibble named hw1_df that contains four variables of different data types.

- **rand_samp** generates a random sample of 10 values drawn from a standard normal distribution (mean = 0, standard deviation = 1)
- **logical_vec** creates a logical vector indicating whether each element in `rand_samp` is greater than 0
- **char_vec** defines a character vector containing 10 distinct animal names
- **factor_vec** creates a factor vector that includes categorical data with three levels

```{r hw1_p2}
hw1_df = tibble(
  rand_samp = rnorm(10),              
  logical_vec = rand_samp > 0,
  char_vec = c("bear", "dog", "cat", "dolphin", "penguin", "cabybara", "llama", "goose", "pigeon", "goat"),
  factor_vec = factor(c("yes", "maybe", "no", "yes", "maybe", "yes", "no", "no", "maybe", "yes"))
)
```

This displays the contents of the dataframe 'hw1_df'.
```{r display_table, echo = FALSE}
print(hw1_df)
```

When trying to return the mean of each variable...

* The mean of the random sample is `r mean(pull(hw1_df, rand_samp))`
* The mean of the logical vector is `r mean(pull(hw1_df, logical_vec))`
* The mean of the character vector is `r mean(pull(hw1_df, char_vec))`
* The mean of the factor vector is `r mean(pull(hw1_df, factor_vec))`

The random sample and logical vector is able to return a mean. However, the character and factor vectors are not able to return a mean because it is neither numeric nor logical.


```{r convert_types, echo = FALSE, warning = FALSE}
numeric_logical_vec = as.numeric(hw1_df$logical_vec)
numeric_char_vec = as.numeric(hw1_df$char_vec)
numeric_factor_vec = as.numeric(hw1_df$factor_vec)
```

```{r list_converted, echo = FALSE, results = "hide", warning = FALSE}
list(
  numeric_logical_vec = numeric_logical_vec,
  numeric_char_vec = numeric_char_vec,
  numeric_factor_vec = numeric_factor_vec
)
```

### Converting variables to numeric
After applying the as.numeric function to the logical, character, and factor variables, the logical and factor vectors were converted to numbers. Logical vector "True" values were converted to 1 and "False" values were converted to 0. The factor vector was converted into numbers to represent the levels of the factor (no, yes, maybe). However, the conversion was misleading because the conversion was not meaningful. The character vectors result in NA values because each character could not be interpreted as numbers.

This explains why the mean was not returned for character and factor vector variables because these data types do not have a numeric representation that allows for conversion.