---
title: "p8105_hw1_sd3730"
author: "Stacey Dai"
output: github_document
---

```{r setup, include = FALSE}
library(tidyverse)
data("penguins", package = "palmerpenguins")
```


# Problem 1

The `penguins` dataset contains information about the measurements of penguins. There are `r nrow(penguins)` rows and `r ncol(penguins)` columns in the dataset. Some important variables include:

- `species`: The species of the penguins, such as `r paste(unique(penguins$species), collapse = ", ")`.
- `island`: The island where the penguins were observed (`r paste(unique(penguins$island), collapse = ", ")`).

Other variables include `bill_length_mm` and `bill_depth_mm`, which describe the length and depth of the bills of penguins in millimeters, respectively. The variable `sex` refers to the gender of the penguins and `year` represents the year that the penguin data was collected. 

The variable `flipper_length_mm` represents the length of the penguins' flippers in millimeters. The mean flipper length is `r mean(penguins$flipper_length_mm, na.rm = TRUE)` mm.

## Scatterplot of flipper length by bill length
```{r yx_scatter, warning = FALSE}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + 
  geom_point()
```

```{r save-plot, echo = FALSE, warning = FALSE}
ggsave("penguins_scatterplot.png", height = 4, width = 6)
```


# Problem 2

This code creates a tibble named hw1_df that contains four columns of mixed data types for analysis.

```{r hw1_p2}
hw1_df = tibble(
  rand_samp = rnorm(10),              
  logical_vec = rand_samp > 0,
  char_vec = c("bear", "dog", "cat", "dolphin", "penguin", "cabybara", "llama", "goose", "pigeon", "goat"),
  factor_vec = factor(c("yes", "maybe", "no", "yes", "maybe", "yes", "no", "no", "maybe", "yes"))
)
```

This is the dataframe output.
```{r display_table, echo = FALSE}
print(hw1_df)
```

When trying to return the mean of each variable...

* The mean of the random sample is `r mean(pull(hw1_df, rand_samp))`
* The mean of the logical vector is `r mean(pull(hw1_df, logical_vec))`
* The mean of the character vector is `r mean(pull(hw1_df, char_vec))`
* The mean of the factor vector is `r mean(pull(hw1_df, factor_vec))`

The random sample and logical vector is able to return a mean. However, the character and factor vectors are not able to return a mean because it is neither numeric nor logical.

```{r convert_types, echo = FALSE, warning = FALSE}
numeric_logical_vec = as.numeric(hw1_df$logical_vec)
numeric_char_vec = as.numeric(hw1_df$char_vec)
numeric_factor_vec = as.numeric(hw1_df$factor_vec)
```


```{r list_converted, echo = FALSE, warning = FALSE}
list(
  numeric_logical_vec = numeric_logical_vec,
  numeric_char_vec = numeric_char_vec,
  numeric_factor_vec = numeric_factor_vec
)
```

After converting the logical, character, and factor variables to numeric, the logical and factor vectors are converted to numbers. "True" values are converted to 1 and "False" values are converted to 0. The factor vector is converted into numbers to represent the levels of the factor (no, yes, maybe). However, the conversion can be misleading because the conversion is not meaningful. The character vectors still result in NA values because each character cannot be interpreted as numbers.
